%!TEX root = ../username.tex
\chapter{Conclusion and Future Work} \label{chap:conclusion}

In this study, we assess the performance of R-CNN and YOLOv5 models for object detection in traffic scenes using pre-trained weights for the COCO 80 labels dataset. However, as we did not train these models specifically for the traffic scene domain, the reported performance may not fully reflect their potential for autonomous vehicle applications. Unfortunately, we were unable to train these models ourselves due to the lack of access to GPU hardware. Therefore, we recommend the next step to be training these models for traffic detection using the software proposed in this study to re-evaluate their performance. Additionally, we could not experiment with YOLOv7, which is an improvement over YOLOv5 with the capability to perform instance segmentation, due to our hardware limitation issue. Comparing Mask R-CNN and YOLOv7 on both object detection and instance segmentation tasks can be a meaningful experiment for the future.

This study covers various computer vision tasks, with a focus on object detection and instance segmentation algorithms, and their applications in autonomous driving. A detailed explanation of the backbone Convolution Neural Network is also provided. Additionally, we discuss the evolution of the R-CNN and YOLO model families and how they improve through each iteration. We followed by a detail explained and example for the metrics used to evaluate these models. Finally, all this knowledge is applied to develop a comparison software between the Mask R-CNN and YOLOv5 models for detecting pedestrians and vehicles in traffic scenes.